Learned image compression

### 2023-03-14 paper/paper.tex
Fix tables

\begin{center}
\caption{Table \ref{table:architecture}: Architecture of ELIC-sm main transform networks. \cite{ELIC}}\\
\begin{tabular}{l|l}
\hline
Analyzer $g_a$ & Synthesizer $g_s$ \\
\hline
in: 3-channel image & in: M-channel symbols \\
\hline
Conv 5 $\times$ 5, s2, N & TConv 5 $\times$ 5, s2, N \\
ResBottleneck$\times$1 & ResBottleneck$\times$1 \\
Conv 5 $\times$ 5, s2, N & TConv 5 $\times$ 5, s2, N \\
ResBottleneck$\times$1 & ResBottleneck$\times$1 \\
Conv 5 $\times$ 5, s2, N & TConv 5 $\times$ 5, s2, N \\
ResBottleneck$\times$1 & ResBottleneck$\times$1 \\
Conv 5 $\times$ 5, s2, M & TConv 5 $\times$ 5, s2, 3 \\
\hline
\end{tabular}
\label{table:architecture}
\end{center}

@@

\begin{center}
\caption{Table \ref{table:SCCTX}: Number of trainable parameters in SCCTX in\\ thousands for each block ($b_i$) and for each component.}\\
\begin{tabular}{c c c c c c c} 
 \hline
 _ & b_0 & b_1 & b_2 & b_3 & b_4 & sum \\  
 \hline\hline
 channel & \textit{NaN} & 26 & 103 & 410 & 512 & 1050 \\
 \hline
 spatial & 13 & 13 & 51 & 205 & 205 & 487 \\
 \hline
 par.agg. & 198 & 198 & 277 & 480 & 480 & 1632 \\
 \hline
 sum & 210 & 236 & 431 & 1095 & 1197 & 3169 \\
 \hline
\end{tabular}
\label{table:SCCTX}
\end{center}

>>>>

\begin{table}[!h]
\label{table:architecture}
\begin{center}
\caption{Architecture of ELIC-sm main transform networks. \cite{ELIC}}
\begin{tabular}{l|l}
\hline
Analyzer $g_a$ & Synthesizer $g_s$ \\
\hline
in: 3-channel image & in: M-channel symbols \\
\hline
Conv 5 $\times$ 5, s2, N & TConv 5 $\times$ 5, s2, N \\
ResBottleneck$\times$1 & ResBottleneck$\times$1 \\
Conv 5 $\times$ 5, s2, N & TConv 5 $\times$ 5, s2, N \\
ResBottleneck$\times$1 & ResBottleneck$\times$1 \\
Conv 5 $\times$ 5, s2, N & TConv 5 $\times$ 5, s2, N \\
ResBottleneck$\times$1 & ResBottleneck$\times$1 \\
Conv 5 $\times$ 5, s2, M & TConv 5 $\times$ 5, s2, 3 \\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[!h]
\label{table:SCCTX}
\begin{center}
\caption{Number of trainable parameters in SCCTX in\\ thousands for each block ($b_i$) and for each component.}
\begin{tabular}{c c c c c c c} 
 \hline
  & $b_0$ & $b_1$ & $b_2$ & $b_3$ & $b_4$ & sum \\
 \hline\hline
 channel & \textit{NaN} & 26 & 103 & 410 & 512 & 1050 \\
 \hline
 spatial & 13 & 13 & 51 & 205 & 205 & 487 \\
 \hline
 par.agg. & 198 & 198 & 277 & 480 & 480 & 1632 \\
 \hline
 sum & 210 & 236 & 431 & 1095 & 1197 & 3169 \\
 \hline
\end{tabular}
\end{center}
\end{table}
